Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election

### 2024-11-02 paper/paper.qmd
1. all /cloud/project/ part in path for writing file or reading file are removed. 2. incorrect link in thanks part of paper changed 3. analysis dataset both saved in parquet file, and according .csv file removed.

---
title: "Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election"
subtitle: "Decoding the dynamics and biases behind Trump's Approval Ratings with polling Data"
author: 
  - Chenming Zhao
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder).
        We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis. The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
date: today
date-format: long
abstract: "This study aims to use a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S. presidential election based on support rates. By analyzing data of 2024 US presidential general election polls across states, pollsters, and methodologies, we capture variations in support for Trump driven by these factors. Our results reveal significant differences in support between national and state-level polls, with fluctuations in key swing states potentially influencing the election outcome. There is a dynamic interaction between election results and public opinion trends, and this study provides insights into how various factors influence public sentiment, offering valuable predictions and understanding of voter dynamics in the U.S. election."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{paper/tabularray}
pdf-engine: lualatex
---

@@

analysis_data <- read_parquet(here::here("/cloud/project/data/02-analysis_data/analysis_trump_data.parquet"))
```

@@

first_model <- readRDS(file = here::here("/cloud/project/models/trump_time_model.rds"))

prediction_data <- read_csv(here::here("/cloud/project/data/02-analysis_data/prediction_data.csv"))
```

@@

modelsummary::modelsummary(
  list("First model" = first_model),
  statistic = "mad",
  fmt = 2,
  output = here::here("/cloud/project/paper/model_summary_table.html")
)
```

>>>>

---
title: "Demystifying Votes: A Hierarchical Bayesian Model for Predicting the 2024 US Presidential Election"
subtitle: "Decoding the dynamics and biases behind Trump's Approval Ratings with polling Data"
author: 
  - Chenming Zhao
thanks: "Code and data are available at: [https://github.com/ChenmingZ2000/2024-presidential-polls-analysis-and-forecast.git).
        We gratefully acknowledge FiveThirtyEight for providing the polling data used in this analysis. The data is available at: [https://projects.fivethirtyeight.com/polls/president-general/2024/national/](https://projects.fivethirtyeight.com/polls/president-general/2024/national/)."
date: today
date-format: long
abstract: "This study aims to use a hierarchical Bayesian model to predict whether Donald Trump will win the 2024 U.S. presidential election based on support rates. By analyzing data of 2024 US presidential general election polls across states, pollsters, and methodologies, we capture variations in support for Trump driven by these factors. Our results reveal significant differences in support between national and state-level polls, with fluctuations in key swing states potentially influencing the election outcome. There is a dynamic interaction between election results and public opinion trends, and this study provides insights into how various factors influence public sentiment, offering valuable predictions and understanding of voter dynamics in the U.S. election."
format: pdf
number-sections: true
bibliography: references.bib
header-includes:
  - \usepackage{paper/tabularray}
pdf-engine: lualatex
---

@@

analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_trump_data.parquet"))
```

@@

first_model <- readRDS(file = here::here("models/trump_time_model.rds"))

prediction_data <- read_parquet(here::here("data/02-analysis_data/prediction_data.parquet"))
```

@@

modelsummary::modelsummary(
  list("First model" = first_model),
  statistic = "mad",
  fmt = 2,
  output = here::here("paper/model_summary_table.html")
)
```
